What is disputed on the web?

### 2010-01-30 papers/wicow_claimfinder/claimfinder.tex
Added draft text for applications, conclusion

\x{We are building lots of applications that will use this data set.}
\x{Dispute Finder highlights disputed claims on the web.}
\x{Tell people when audio they hear is disputed.}
\x{Tell people when a source you trust disagrees with others.}
\x{Tell me when a source I read in the past is now disputed.}
\x{Tell me how contentious a topic is.}
\x{Let me explore what is disputed about a particular topic.}
\x{Tell me when something new is disputed about a topic I care about.}
\x{Examine the zeitgeist of disputes.}
\x{Tell me about things that are disputed by the kind of sites I trust.}
\x{We also want to make this data set available to others.}

@@

\x{We can use the web as a corpus to determine what people think is disputed.}

\x{Talk about how we plan to have a much bigger data set in the future. This is just the start.}

>>>>

A corpus of disputed claims could be useful for a variety of applications, including real-time dispute recognition, background dispute analysis agents, and other research tools. Real-time dispute recognition agents could be used, for instance, to alert users when a trusted source disagrees with others, or to provide the user with feedback on how contentious a topic is.

Dispute Finder is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages. Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications. We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation. Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.

Dispute analysis agents that run in the background represent another application we see for a corpus of disputed claims. Such agents could be trained with information regarding the books, journals, and news articles a user reads. It would then be able to alert the user when a previously-read source is now disputed. It could also track a set of topics and tell the user when something new is disputed about a topic. A background dispute analysis agent would serve as an automated research assistant, alerting me when

A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the zeitgeist of disputes. In this way the cultural

Recognizing that these are but a few of the ways in which a disputed claim corpus could be used, we will release this data set to the research community as a whole.

\x{"It will be available for unrestricted use under the XXX license. The dataset can be accessed at http://xxx.intel.com/xxx"}

@@

Our research has shown that the web can be used as a corpus to determine what claims people identify as being disputed. Although it is likely that any specific claim found on the web is not authoritative, the web as a whole aggregates the array of views to be found online.

Furthermore, because individuals express opinions freely online, a snapshot of the disputed claims online can provide valuable insights into the cultural zeitgeist of the time.

Challenges of creating a comprehensive corpus of disputed claims are many, from data quality to deeper natural language processing challenges such as recognizing textual entailment. We address these in part by taking a high-level statistical view of the data.

The possible applications of a corpus of disputed claims are many and varied. These include real-time dispute recognition, autonomous research agents that operate in the background, and sociocultural research.

Using the claim prefix search technique and text processing, we are able to identify

Our data set currently includes approximately 1.2 million records. We intend to expand this by several orders of magnitude, an improvement that will address issues of data sparsity and enable more robust data processing.
